---
title: "DAG"
---

# 1.
```{r}

# Load packages
library(tidyverse)
library(dagitty)
library(ggdag)

parkingDAG <- dagify(
  X ~ Z,
  Y ~ Z,
  Y ~ X,
  coords = list(x = c(Y = 3, Z = 2, X = 1),
                y = c(Y = 0, Z = 1, X = 0)),
  labels = list(X = "Parking Spot",
                Y = "Sales", 
                Z = "Location")
)

# Plot DAG
ggdag(parkingDAG) +
  theme_dag_gray() + # custom theme, can be left out
  geom_dag_point(color = "lightgreen") +
  geom_dag_text(color = "red") +
  geom_dag_edges(edge_color = "blue") +
  geom_dag_label_repel(aes(label = label))

```

# 2.
In the data, you find three variables: satisfaction, follow_ups and subscription. Perform the following steps:\

**regress satisfaction on follow_ups**\


```{r}
customer_sat <- readRDS("../../assignment_data/customer_sat.rds")
lm_followUps <- lm(satisfaction ~ follow_ups, data = customer_sat)
summary(lm_followUps, digits = 3)

```


**regress satisfaction on follow_ups and account for subscription**

```{r}
lm_all <- lm(satisfaction ~., data = customer_sat)
summary(lm_all, digits = 3)

```
# 3.
In the first table, the analysis shows that follow-ups have a very low p-value, indicating a significant impact on satisfaction. The negative estimate suggests that, on average, more follow-ups are associated with lower satisfaction scores.\

However, upon considering the new regression data, it becomes evident that the subscription plan seems to exert a comparatively stronger impact on satisfaction than follow-ups. Specifically, having a premium or premium plus subscription is associated with higher satisfaction, as indicated by their positive estimates. The sign of the follow-ups estimate has also changed, now suggesting that more follow-ups are associated with higher satisfaction.\

This shift in estimates implies that the new subscription variable acts as a confounding variable. To accurately understand the relationship between follow-ups and satisfaction, it becomes essential to condition on the subscription variable. In other words, to draw meaningful conclusions, it is crucial to compare data for the same type of subscription, ensuring that the impact of follow-ups on satisfaction is assessed within each subscription category.\

# 4.
```{r}
df <- as_tibble(customer_sat)

# Not conditioning on subscription
not_cond <- ggplot(df, aes(x = follow_ups, y = satisfaction)) +
  geom_point() +
  stat_smooth(method = "lm", se = F)


# Conditioning on subscription  
cond <- ggplot(df, aes(x = follow_ups, y = satisfaction, color = subscription)) +
  geom_point(alpha = .8) +
  stat_smooth(method = "lm", se = F) +
  theme(legend.position = "right")

not_cond
cond

# DAG

satisf_DAG <- dagify(
  X ~ Z,
  Y ~ Z,
  Y ~ X,
  coords = list(x = c(Y = 3, Z = 2, X = 1),
                y = c(Y = 0, Z = 1, X = 0)),
  labels = list(X = "Follow ups",
                Y = "Satisfaction", 
                Z = "Subscription")
)
# Plot DAG
ggdag(satisf_DAG) +
  theme_dag_gray() + # custom theme, can be left out
  geom_dag_point(color = "lightgreen") +
  geom_dag_text(color = "red") +
  geom_dag_edges(edge_color = "blue") +
  geom_dag_label_repel(aes(label = label))
```


