---
title: "Difference-in-Differences"
---
```{r}
library(tidyverse)
library(dagitty)
library(ggdag)
library(MatchIt)
library(dplyr)

hospdd <- readRDS("../../assignment_data/hospdd.rds")

```
# . Manually computing the mean satisfaction for treated and control hospitals before and after the treatment:

```{r}

# Manually compute differences
# Step 1: Difference between treatment and control group BEFORE treatment
# control group -> hospital ID 19 and above
# treatment group -> hospital ID 18 or less
# treatment begin : from month 4
before_control_A <- hospdd %>%
  filter(hospital > 18, month < 4) %>% 
  pull(satis)
before_treatment_A <- hospdd %>%
  filter(hospital <= 18, month < 4) %>% 
  pull(satis)

diff_before_A <- mean(before_treatment_A) - mean(before_control_A)

# Step 2: Difference between treatment and control group AFTER treatment
after_control_A <- hospdd %>%
  filter(hospital > 18, month >= 4) %>% 
  pull(satis)
after_treatment_A <- hospdd %>%
  filter(hospital <= 18, month >= 4) %>% 
  pull(satis)

diff_after_A <- mean(after_treatment_A) - mean(after_control_A)

# Step 3: Difference-in-differences. 
diff_diff_A <- diff_after_A - diff_before_A
cat("Estimate: ", diff_diff_A)
```



# . Using a linear regression to compute the estimate
In this context, it is important to note that the variables "month" and "hospital" are categorical, and they are not continuous or ordinal variables. Therefore, it is advisable to apply the `as.factor()` function to ensure more accurate computations.
```{r}

summary(lm(satis ~ procedure + as.factor(month) + as.factor(hospital), data = hospdd))

```


